% UC Bio-bib Lectures Table
% Created on 2018-09-24 17:41

\tablehead{Month/Year & Topic & Place/Conference\\ \hline}
\begin{supertabular}{lp{10.0cm}p{4.5cm}}
12/2016 & Using Small Drone (UAS) Imagery to Bridge the Gap Between Field-and Satellite-Based Measurements of Vegetation Structure and Change. Mayes, MT and Estes, LD and Gago, X and Debats, SR and Caylor, KK and Manfreda, S and Oudemans, P and Ciraolo, G and Maltese, A and Nadal, M and others & AGU Fall Meeting Abstracts \\
12/2016 & Linking Carbon Flux Dynamics and Soil Structure in Dryland Soils. DeCarlo, Keita F and Caylor, Kelly K & AGU Fall Meeting Abstracts \\
12/2016 & Characterization of canopy dew formation in tropical forests using active microwave remote sensing. Gerlein-Safdi, C and Frolking, SE and Caylor, KK & AGU Fall Meeting Abstracts \\
12/2016 & An ecohydrologic framework for simulating catchment constraints on smallholder irrigation systems in drylands. Gower, D and McCord, PF and Caylor, KK and Dell'Angelo, J and Evans, TP & AGU Fall Meeting Abstracts \\
12/2016 & Harmonizing Social and Environmental Dynamics in Earth Systems Modeling. Evans, Tom P and Estes, Lyndon D and Caylor, Kelly K and McCord, Paul Frederick and Gower, Drew and Konar, M and Baylis, K and Waldman, K and Blekking, J and Schlachter, T & AGU Fall Meeting Abstracts \\
12/2016 & Combining Human and Machine Learning to Map Cropland in the 21st Century's Major Agricultural Frontier. Estes, Lyndon D and Debats, SR and Caylor, Kelly K and Evans, Tom P and Gower, Drew and McRitchie, Dennis and Searchinger, Timothy and Thompson, David R and Wood, Eric F and Zeng, Lindy & AGU Fall Meeting Abstracts \\
12/2016 & Rapid Monitoring of Drought Impacts on Small-Scale Farms in Africa through Integration of Farmer SMS data and Environmental Sensors. Evans, Tom P and Caylor, Kelly K and Estes, Lyndon D and Plale, Beth A and Attari, Shahzeen and Waldman, Kurt & AGU Fall Meeting Abstracts \\
12/2016 & Can we forecast farmers' yields? The relationships between rainfall variability, farmers' expectations, and actual yields in a tropical dryland. Zeng, Z and Tian, D and Estes, LD and Evans, TP and Wood, EF and Caylor, KK & AGU Fall Meeting Abstracts \\
12/2016 & Assessment of SMAP L2/L3 Soil Moisture Products using In Situ Based Core Validation Sites. Colliander, A and Jackson, TJ and Bindlish, R and Chan, S and Das, NN and Kim, S and Cosh, MH and Dunbar, RS and Asanuma, J and Aida, K and others & AGU Fall Meeting Abstracts \\
2/2017 & Invited Speaker, Session on ``Hydrologic connectivity: linking land use changes and management to movement and transformations of resources within catchments'' &  ALSO Annual Aquatic Sciences Meeting \\
10/2017 & Seminar Speaker, Department of Plant Sciences Seminar & University of California, Riverside \\
12/2017 & Is deciduousness a key to climate resilience among iconic California savanna oak species? Relating phenological habits to seasonal indicators of tree physiological and water stress across field, hyperspectral, drone (UAS)-based multispectral and thermal image data. Mayes, MT and Caylor, KK and Ehlmann, BL and Greenberger, RN and Estes, LD & AGU Fall Meeting Abstracts \\
12/2017 & High spatial resolution mapping of land cover types in a priority area for conservation in the Brazilian savanna. Ribeiro, F and Roberts, DA and Hess, LL and Davis, FW and Caylor, KK and Nackoney, J and Antunes Daldegan, G & AGU Fall Meeting Abstracts \\
12/2017 & Simulating the impact of water storage on agricultural intensification and deforestation in Northern Thailand. Gower, D and Zeng, Z and Caylor, KK and Wood, EF & AGU Fall Meeting Abstracts \\
12/2017 & Effects of dew deposition on transpiration and carbon uptake in leaves. Gerlein-Safdi, C and Koohafkan, M and Chung, M and Rockwell, FE and Thompson, SE and Caylor, KK & AGU Fall Meeting Abstracts \\
12/2017 & Real-time monitoring of smallholder farmer responses to intra-seasonal climate variability in central Kenya. Krell, N and Evans, TP and Estes, LD and Caylor, KK & AGU Fall Meeting Abstracts \\
4/2018 & Invited Speaker, Workshop on Spatial Pattern Formation in Ecosystems & Princeton University, Center for Theoretical Science \\
4/2018 & On the use of unmanned aerial systems for environmental monitoring. Manfreda, S., Ben Dor, E., Caylor, K.K., Ciraolo, G., De Lima, I., De Lima, J.L.M., Estes, L., Frances, F., Helman, D., Kohv, M., Lucas, R., Madrigal, V.P., Mallinis, G., Maltese, A., McCabe, M., Miller, P., Perks, M., Ruiz-Perez, G., Tauro, F., Toth, B. & European Geosciences Union, General Assembly 
 \\
4/2018 & Integrating humans and machines to map smallholder-dominated agricultural frontiers. Estes, L., Caylor, K.K., Debats, S., Eastman, R., Thompson, D.R.  & Association of American Geographers Annual Meeting \\
4/2018 & Towards assessing urban food security and nutrition in West Africa. Tuholske, C., Andam, K., Blekking, J., Caylor, K., Evans, T. & American Association of Geographers Annual Meeting  \\
\end{supertabular}

