% UC Bio-bib Publication Table
% Created on 2018-10-10 23:23

\begin{longtable}{lcp{7.75cm}>{\raggedright}p{5.25cm}p{1.75cm}}
\# & Year & Title and Authors & Publisher & Category\\
\hline 
\endhead 
1 & 2000 & {\bf Approaches for the estimation of primary productivity and vegetation structure in the Kalahari region }, Dowty, P.R., Caylor, K.K., Shugart, H.H,, Emanuel, W.R. & Ringrose, S., Chanda, R. (eds.). \emph{ Towards Sustainable Natural Resource Management in the Kalahari Region.  }. University of Botswana Press & Refereed Book Chapter\\
2 & 2002 & {\bf The southern African Regional Science Initiative (SAFARI 2000): Wet season campaigns}, Otter, LB, Scholes, RJ, Dowty, PR, Privette, JP, Caylor, K.K., Ringrose, S, Mukelabai, M, Frost, P, Hanan, N, Totolo, O, Veenendall, EM. \href{https://ucsb.box.com/s/b6gdsjokzr9s3c517rc0wzuciokb9ed2}{[pdf]} & \emph{ South African Journal of Science } 98(3-4): 131-137.   & Refereed Article\\
3 & 2002 & {\bf Determining land surface fractional cover from NDVI and rainfall time series for a savanna ecosystem}, Scanlon, TM, Albertson, JD, Caylor, K.K., Williams, CA. \href{https://ucsb.box.com/s/olehfbnhdp7jfr62haar256je6stllzc}{[pdf]} & \emph{ Remote Sensing of Environment } 82(2-3): 376-388.   & Refereed Article\\
4 & 2002 & {\bf Trends in savanna structure and composition on an aridity gradient in the Kalahari}, Scholes, RJ, Dowty, PR, Caylor, K.K., Parsons, DAB, Frost, PGH, Shugart, HH. \href{https://ucsb.box.com/s/ieihhqenol65p5q91ntqjfys52wp5q8z}{[pdf]} & \emph{ Journal of Vegetation Science } 13(3): 419-428.   & Refereed Article\\
5 & 2003 & {\bf Tree spacing along the Kalahari transect in southern Africa}, Caylor, K.K., Shugart, HH, Dowty, PR, Smith, TM. \href{https://ucsb.box.com/s/i31hw7ssrpmxqnno5iz5wdzp8wqy1df8}{[pdf]} & \emph{ Journal of Arid Environments } 54(2): 281-296.   & Refereed Article\\
6 & 2003 & {\bf Release of gaseous and particulate carbonaceous compounds from biomass burning during the SAFARI 2000 dry season field campaign}, Hely, C, Caylor, K.K., Alleaume, S, Swap, RJ, Shugart, HH. \href{https://ucsb.box.com/s/jztfplnyhywtwh6ipki4pkcn3txghbro}{[pdf]} & \emph{ Journal of Geophysical Research - Atmospheres } 108(13).   & Refereed Article\\
7 & 2003 & {\bf Regional fuel load for two climatically contrasting years in southern Africa}, Hely, C, Dowty, PR, Alleaume, S, Caylor, K.K., Korontzi, S, Swap, RJ, Shugart, HH, Justice, CO. \href{https://ucsb.box.com/s/36fbprbjg0ba8945fedk5xicnccg4urx}{[pdf]} & \emph{ Journal of Geophysical Research - Atmospheres } 108(13).   & Refereed Article\\
8 & 2003 & {\bf Soil moisture and plant stress dynamics along the Kalahari precipitation gradient}, Porporato, A, Laio, F, Ridolfi, L, Caylor, K.K., Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/wmif3on87b64h7ra309i1m093qxtkxtl}{[pdf]} & \emph{ Journal of Geophysical Research - Atmospheres } 108(D3).   & Refereed Article\\
9 & 2004 & {\bf Coupling ecohydrological patterns and processes in semi-arid landscapes}, Caylor, K.K., Rodriguez-Iturbe, I &  \emph{ Proceedings of the British Hydrological Society's International Conference on Hydrology: Science \& Practice for the 21st Century }. British Hydrological Society & Refereed Conference Proceedings\\
10 & 2004 & {\bf Simulated productivity of heterogeneous patches in Southern African savanna landscapes using a canopy productivity model}, Caylor, K.K., Shugart, HH. \href{https://ucsb.box.com/s/lxzxkmnl6k7duxinlgvg1qfavzph97ei}{[pdf]} & \emph{ Landscape Ecology } 19(4): 401-415.   & Refereed Article\\
11 & 2004 & {\bf Feasible optimality of vegetation patterns in river basins}, Caylor, K.K., Scanlon, TM, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/55r8uw1o2a4irc57noharl7mfa6xrivf}{[pdf]} & \emph{ Geophysical Research Letters } 31(13). doi:10.1029/2004GL020260.  & Refereed Article\\
12 & 2004 & {\bf Relationship between small-scale structural variability and simulated vegetation productivity across a regional moisture gradient in southern Africa}, Caylor, K.K., Dowty, PR, Shugart, HH, Ringrose, S. \href{https://ucsb.box.com/s/vdafumcv2fqobshrxsrheaaskst3w57f}{[pdf]} & \emph{ Global Change Biology } 10(3): 374-382.   & Refereed Article\\
13 & 2004 & {\bf Vegetation structure characteristics and relationships of Kalahari woodlands and savannas}, Privette, JP, Tian, Y, Roberts, G, Scholes, RJ, Wang, Y, Caylor, K.K., Mukelabai, M. \href{https://ucsb.box.com/s/9v3epeslmv63b8aro7776cx4miuh7c8p}{[pdf]} & \emph{ Global Change Biology } 10(3): 281-291.   & Refereed Article\\
14 & 2004 & {\bf A  simulation analysis of the detectability of understory burns in miombo woodlands}, Pereira, JMC, Mota, B, Privette, JL, Caylor, K.K., Silva, JMN, Sa, ACL, Ni-Meister, W. \href{https://ucsb.box.com/s/twwp4rpdj4zkj7r2t63lmb164o704zgs}{[pdf]} & \emph{ Remote Sensing of Environment } 93(3): 296-310.   & Refereed Article\\
15 & 2005 & {\bf Tree canopy effects on simulated water stress in southern African savannas}, Caylor, K.K., Shugart, HH, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/8797xcvvxovh01qx1np314yu5do9slhg}{[pdf]} & \emph{ Ecosystems } 8(1): 106-121. doi:10.1007/s10021-004-0027-9.  & Refereed Article\\
16 & 2005 & {\bf On the coupled geomorphological and ecohydrological organization of river basins}, Caylor, K.K., Manfreda, S., Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/y6synn1tov8586n8nrnbsp59w58nyieg}{[pdf]} & \emph{ Advances in Water Resources } 28(1): 69-86. doi:10.1016/j.advwatres.2004.08.013.  & Refereed Article\\
17 & 2005 & {\bf Dynamic response of grass cover to rainfall variability: Implications for the function and persistence of savanna ecosystems}, Scanlon, TM, Caylor, K.K., Manfreda, Salvatore, Levin, Simon, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/2mlqvq04i8bm5rzct19de60mm08b3nl5}{[pdf]} & \emph{ Advances in Water Resources } 28(3): 291-302. doi:10.1016/j.advwatres.2004.10.014.  & Refereed Article\\
18 & 2005 & {\bf Determinants of woody cover in African savannas: A continental scale analysis}, Sankaran, M, Hanan, N, Scholes, B, Ratnam, Jayashree, 24 others, Caylor, K.K.. \href{https://ucsb.box.com/s/y6synn1tov8586n8nrnbsp59w58nyieg}{[pdf]} & \emph{ Nature } 438(7069): 846. doi:10.1038/nature04070.  & Refereed Article\\
19 & 2006 & {\bf Dynamic change in the woodland and savanna ecosystems of sub-tropical Africa. }, Shugart, H.H, Caylor, K.K., Hely, C., Swap, R.J., Dowty, P.R. & Laurence, W., Peres, C. (eds.). \emph{ Emerging Threats to Tropical Forests }. University of Chicago Press & Refereed Book Chapter\\
20 & 2006 & {\bf Pattern and process in savanna ecosystems}, Caylor, K.K, Shugart, H.H. & D'Odorico, P., Porporato, A. (eds.). \emph{ Dryland Ecohydrology }. Springer & Refereed Book Chapter\\
21 & 2006 & {\bf On the ecohydrology of structurally heterogeneous semi-arid landscapes}, Caylor, K.K., D'Odorico, P, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/tdvp7iyzjqw27m4p4l0qznq2u512x5f7}{[pdf]} & \emph{ Water Resources Research } 42(7). doi:10.1029/2005WR004683.  & Refereed Article\\
22 & 2007 & {\bf Ecohydrological optimization of patterns and processes in water-limited ecosystems.}, Caylor, K.K., Scanlon, T.M., Rodriguez-Iturbe, I. &  \emph{ Water and the Environment: Proceedings of the Workshop in the Vatican Academy of Sciences. }. Vatican Academy of Sciences & Refereed Conference Proceedings\\
23 & 2007 & {\bf A temporal and spatially explicit Production Efficiency Model for fuel load allocation in southern Africa}, Hely, C, Caylor, K.K., Dowty, PR, Alleaume, S, Swap, RJ, Shugart, HH, Justice, CO. \href{https://ucsb.box.com/s/mtsd3uey6jmrffgggwfky0jksjzgd3yo}{[pdf]} & \emph{ Ecosystems } 10(7): 1116. doi:10.1007/s10021-007-9082-3.  & Refereed Article\\
24 & 2007 & {\bf Spatial variation in vegetation structure coupled to plant available water at landscape scales in a Brazilian savanna}, Ferira, J., Bustamente, M, Garcia-Montiel, DC, Caylor, K.K., Davidson, EA. \href{https://ucsb.box.com/s/u35flxwby4qwpnistwyslfe6kt9cnjsx}{[pdf]} & \emph{ Oecologia } 153(2): 417-430. doi:10.1007/s00442-007-0747-6.  & Refereed Article\\
25 & 2007 & {\bf When is breeding for drought tolerance optimal when drought is random?}, Sambatti, J, Caylor, K.K.. \href{https://ucsb.box.com/s/tnajwihyo5ne50s0bsot15cvpyuypspe}{[pdf]} & \emph{ New Phytologist } 175(1): 70-80. doi:10.1111/j.1469-8137.2007.02067.x.  & Refereed Article\\
26 & 2007 & {\bf On soil moisture–vegetation feedbacks and their possible effects on the dynamics of dryland ecosystems}, D'Odorico, P, Caylor, K.K., Okin, GS, Scanlon, TM. \href{https://ucsb.box.com/s/vwn5pfu2jgkou99j85jmsg2vrpw83y3k}{[pdf]} & \emph{ Journal of Geophysical Research - Biogeosciences } 112(G4).   & Refereed Article\\
27 & 2007 & {\bf Positive feedbacks promote power-law clustering of Kalahari vegetation}, Scanlon, TM, Caylor, K.K., Levin, Simon, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/s9w8rphgkh4c5dyukac0kxn5aai1pawx}{[pdf]} & \emph{ Nature } 449(7159): 209. doi:10.1038/nature06060.  & Refereed Article\\
28 & 2008 & {\bf Spatial patterns of soil nutrients in two southern African savannas}, Okin, GS, Mladenov, N, Wang, L, Cassel, D, Caylor, K.K., Ringrose,S. \href{https://ucsb.box.com/s/n2ldvitpqqsxq37llazh9mju12hth7ce}{[pdf]} & \emph{ JGR - Biogeosciences } 113(G2). doi:10.1029/2007JG000584.  & Refereed Article\\
29 & 2009 & {\bf Decoupling structural and environmental determinants of sap velocity}, Dragoni, D., Caylor, K.K. &  \emph{ Proceedings of the 7th International Workshop on Sap Flow, Seville, Spain }. Acta Horticulture & Refereed Conference Proceedings\\
30 & 2009 & {\bf On the calibration of continuous, high-precision $\delta$18O and $\delta$2H measurements using an off-axis integrated cavity output spectrometer }, Wang, L, Caylor, K.K., Dragoni, D.. \href{https://ucsb.box.com/s/emkuq3fane0kbkz1ddl68zdj6q2mx4mn}{[pdf]} & \emph{ Rapid Communications in Mass Spectrometry } 23(4): 530-536. doi:10.1002/rcm.3905.  & Refereed Article\\
31 & 2009 & {\bf Ecohydrological optimization of pattern and process in dryland ecosystems: A tradeoff-based hypothesis}, Caylor, K.K., Scanlon, TM, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/845xm9m13t6m2cly77j3i19w2xf02b2n}{[pdf]} & \emph{ Water Resources Research } 45(8). doi:10.1029/2008WR007230.  & Refereed Article\\
32 & 2009 & {\bf Decoupling structural and environmental determinants of sap velocity: Part II, Observational application}, Dragoni, D, Caylor, K.K., Schmid, H. \href{https://ucsb.box.com/s/tb6bdp2c2rdn0t1rq67hdl8pwqj3m6h1}{[pdf]} & \emph{ Agriculture \& Forest Meteorology } 149(3-4): 570-581. doi:10.1016/j.agrformet.2008.10.006.  & Refereed Article\\
33 & 2009 & {\bf Decoupling structural and environmental determinants of sap velocity: Part I, Methodological development}, Caylor, K.K., Dragoni, D.. \href{https://ucsb.box.com/s/lacmxbi8aa8hb1v42r31gtwg7i9sdhlv}{[pdf]} & \emph{ Agriculture \& Forest Meteorology } 149(3-4): 559-569. doi:10.1016/j.agrformet.2008.10.010.  & Refereed Article\\
34 & 2009 & {\bf Spatial heterogeneity and sources of soil carbon in Southern African savannas}, Wang, L, Okin, G., Caylor, K.K., Macko, S. \href{https://ucsb.box.com/s/szp8sk6zqwly0av56jn4f0bzcitkgu9a}{[pdf]} & \emph{ Geoderma } 149(3-4): 402-408.   & Refereed Article\\
35 & 2010 & {\bf Combined effect of soil moisture and nitrogen availability variations on grass productivity in African savannas}, Wang, L, D'Odorico, P, Ries, L., Caylor, K.K., Macko, S. \href{https://ucsb.box.com/s/5g5my565pfyu35e7di3nhomo6v9io6hc}{[pdf]} & \emph{ Plant \& Soil } 328(1-2): 95-108. doi:10.1007/s11104-009-0085-z.  & Refereed Article\\
36 & 2010 & {\bf Nutrient limitation on above-ground grass production in four savanna types along the Kalahari Transect}, Ries-O'Halloran, L, Shugart, HH, Wang, L, Caylor, K.K., Ringrose, S. \href{https://ucsb.box.com/s/8ce51wudcyvbalnvu9g0zld9e3mz8qrx}{[pdf]} & \emph{ Journal of Arid Environments } 74(2): 284-290. doi:10.1016/j.jaridenv.2009.08.012.  & Refereed Article\\
37 & 2010 & {\bf An ecohydrological approach to  predict regional species distribution patterns in dryland ecosystems}, Franz, T., Caylor, K.K., Rodriguez-Iturbe, I. , Celia, M., Norbotton, J. \href{https://ucsb.box.com/s/3rtg5n9k01htohse3ek4uqrcjxscjavw}{[pdf]} & \emph{ Advances in Water Resources } 33(2): 215-230. doi:10.1016/j.advwatres.2009.12.003.  & Refereed Article\\
38 & 2010 & {\bf On the importance of accurate depiction of infiltration processes on model soil moisture and vegetation water stress}, Manfreda, S., Scanlon, TM, Caylor, K.K.. \href{https://ucsb.box.com/s/7l91zvvz8qbd3rd18imbdr9cvr5lz579}{[pdf]} & \emph{ Ecohydrology } 3(2): 155-165. doi:10.1002/eco.79.  & Refereed Article\\
39 & 2010 & {\bf Partitioning evapotranspiration across gradients of woody plant cover: assessment of a stable isotope technique}, Wang, L, Caylor, K.K., Villegas, J.C., Barron-Gafford, G, Breshears, DD, Huxman, T. \href{https://ucsb.box.com/s/mnuqkwhfrdwozz5phl943aocba8dcmav}{[pdf]} & \emph{ Geophysical Research Letters } 37(9). doi:10.1029/2010GL043228.  & Refereed Article\\
40 & 2010 & {\bf Herbivores and mutualistic ants interact to regulate tree photosynthesis}, King, E.G., Caylor, K.K.. \href{https://ucsb.box.com/s/97zesjj4toiug1ku8awt6geh4423q635}{[pdf]} & \emph{ New Phytologist } 187(1): 17-21. doi:10.1111/j.1469-8137.2010.03286.x.  & Refereed Article\\
41 & 2011 & {\bf Quantifying Transient Soil Moisture Dynamics Using Multipoint Direct-Current Resistivity in Homogeneous Sand}, Franz, T., Nolan, J, Nordbotten, J, Caylor, K.K., Slater, L.. \href{https://ucsb.box.com/s/blycewacm6l92ypovq9nj776fegfujqv}{[pdf]} & \emph{ Vadose Zone Journal } 10(1): 286-298. doi:10.2136/vzj2010.0031.  & Refereed Article\\
42 & 2011 & {\bf Climatological determinants of woody cover in Africa}, Good, S.P., Caylor, K.K.. \href{https://ucsb.box.com/s/ph7ye2bb98cgnxi09bru3h7u8z7hrad0}{[pdf]} & \emph{ Proceedings of the National Academy of Sciences } 108(12): 4902-4907. doi:10.1073/pnas.1013100108.  & Refereed Article\\
43 & 2011 & {\bf Coupling vegetation organization patterns to soil resource heterogeneity in a central Kenyan dryland using geophysical imagery}, Franz, T., King, E.G., Caylor, K.K., Robinson, DA. \href{https://ucsb.box.com/s/4j25lj1ogqflsythbmphe17jc9efxxw3}{[pdf]} & \emph{ Water Resources Research } 47(7). doi:10.1029/2010WR010127.  & Refereed Article\\
44 & 2011 & {\bf Metabolic principles of river basin organization}, Rodriguez-Itrube, I, Caylor, K.K., Rinaldo, A.. \href{https://ucsb.box.com/s/ys07p6ohb73r0lt3x8ue4wzkmehkdvs9}{[pdf]} & \emph{ Proceedings of the National Academy of Sciences } 108(29): 11751-11755. doi:10.1073/pnas.1107561108.  & Refereed Article\\
45 & 2011 & {\bf Ecohydrology in Practice: Strengths, Conveniences, and Opportunities}, King, E.G., Caylor, K.K.. \href{https://ucsb.box.com/s/akdvjq4ad8xtiawy78c2bamqccaf4hr0}{[pdf]} & \emph{ Ecohydrology } 4(4): 608-612. doi:10.1002/eco.248.  & Refereed Article\\
46 & 2012 & {\bf An ecohydrological approach to predicting hillslope-scale vegetation patterns in dryland ecosystems}, Franz, T., Caylor, K.K., King, E.G., Nordbotten, J, Celia, MA, Rodriguez-Iturbe, I. \href{https://ucsb.box.com/s/4j25lj1ogqflsythbmphe17jc9efxxw3}{[pdf]} & \emph{ Water Resources Research } 48(1). doi:10.1029/2011WR010524.  & Refereed Article\\
47 & 2012 & {\bf Multi-sensor derivation of regional vegetation fractional cover in Africa}, Guan, K., Wood, E.F., Caylor, K.K.. \href{https://ucsb.box.com/s/r84mzs2sd3tunyspr2n1pf6jvsl6qttp}{[pdf]} & \emph{ Remote Sensing of Environment } 124: 653-665. doi:10.1016/j.rse.2012.06.005.  & Refereed Article\\
48 & 2012 & {\bf Characterizing ecohydrological and biogeochemical connectivity across multiple scales: a new conceptual framework}, Wang, L., Zou, Chris, O'Donnell, F., Good, S., Franz, T., Miller, G.R., Caylor, K.K.. \href{https://ucsb.box.com/s/0ih6dau65nfez1mza4j8cd145i61abt4}{[pdf]} & \emph{ Ecohydrology } 5(2): 221-233. doi:10.1002/eco.1187.  & Refereed Article\\
49 & 2012 & {\bf Ecohydrological interactions in a two-phase mosaic dryland: implications for regime shifts, resilience, and restoration}, King, E.G., Franz, T., Caylor, K.K.. \href{https://ucsb.box.com/s/ycl4jflncrn9jijcposeu7lqp9nhn95b}{[pdf]} & \emph{ Ecohydrology } 5(6): 733-745. doi:10.1002/eco.260.  & Refereed Article\\
50 & 2012 & {\bf Direct quantification of leaf transpiration isotopic composition}, Wang, L, Good, S.P., Caylor, K.K.. \href{https://ucsb.box.com/s/tpdda6gz6749vps3gprhdoxgc2zxqvta}{[pdf]} & \emph{ Agriculture \& Forest Meteorology } 154: 127-135. doi:10.1016/j.agrformet.2011.10.018.  & Refereed Article\\
51 & 2012 & {\bf A model-based evaluation of woody plant encroachment impacts on coupled carbon and water cycles}, O'Donnell, Caylor, K.K.. \href{https://ucsb.box.com/s/bp0wbewjc99buddxye728fh874kl3lp6}{[pdf]} & \emph{ Journal of Geophysical Research - Biogeosciences } 117(G2). doi:10.1029/2011JG001899.  & Refereed Article\\
52 & 2012 & {\bf Understanding the role of ecohydrological feedbacks in ecosystem-state change in drylands}, Turnbull, L, Wilcox, B.P., Belnap, J, Ravi, S, others, Caylor, K.K.. \href{https://ucsb.box.com/s/p3ra3eesr9ri9hbup1ji51zewx973qvt}{[pdf]} & \emph{ Ecohydrology } 5(2): 174-183. doi:10.1002/eco.265.  & Refereed Article\\
53 & 2012 & {\bf Evaluating ecohydrological theories of woody root distribution in the Kalahari}, Bhattachan, A. , Dintwe, K., Tathlego, M., O'Donnell, F., Caylor, K.K., et al.. \href{https://ucsb.box.com/s/pt5mggx0ho7grlm5v3j5q92intkd2bao}{[pdf]} & \emph{ PLoS One } 7(3): e33996. doi:10.1371/journal.pone.0033996.  & Refereed Article\\
54 & 2012 & {\bf Uncertainties in the assessment of the isotopic composition of surface fluxes: A direct comparison of techniques using laser--based water vapor isotope analyzers}, Good, S.P., Soderberg, K., Wang, L, Caylor, K.K.. \href{https://ucsb.box.com/s/e0nqzs1iui7qjw2enl98kjm73f320s0q}{[pdf]} & \emph{ Journal of Geophysical Research - Atmospheres } 117(D5). doi:10.1029/2011JD017168.  & Refereed Article\\
55 & 2012 & {\bf Reframing hydrology education to solve coupled human and environmental problems}, King, E.G., O'Donnell, F., Caylor, K.K.. \href{https://ucsb.box.com/s/wlve0670ia4viq4tj3ai8peitvg30mw6}{[pdf]} & \emph{ Hydrology and Earth System Science } 16(8): 2293-2404. doi:10.5194/hess-16-4023-2012.  & Refereed Article\\
56 & 2012 & {\bf Stable isotopes of water vapor in the vadose zone: A review of measurement and modeling techniques 
}, Soderberg, K., Good, S.P., Wang, L, Caylor, K.K.. \href{https://ucsb.box.com/s/k197xi9q69aakxc4ujsgyw246hqevtdv}{[pdf]} & \emph{ Vadose Zone Journal } 11(3). doi:10.2136/vzj2011.0165.  & Refereed Article\\
57 & 2012 & {\bf Dryland ecohydrology and climate change: critical issues and technical advances }, Wang, L, D'Odorico, P, Evans, J, Eldridge, T., McCabe, M, Caylor, K.K.. \href{https://ucsb.box.com/s/yyb42ibw0fdb8k0i55wsmrau2bb9yf4w}{[pdf]} & \emph{ Hydrology and Earth System Science } 16(8): 2585-2603. doi:10.5194/hess-16-2585-2012.  & Refereed Article\\
58 & 2013 & {\bf Seasonal coupling of canopy structure and function in African tropical forests and its environmental controls}, Guan, K., Wolf, A, Medvigy, David, Caylor, K.K., Pan, Ming, Wood, E.F.. \href{https://ucsb.box.com/s/g281d4dvfhe9pdqzjosrdx06vev53ivk}{[pdf]} & \emph{ Ecosphere } 4(3): 1-21. doi:10.1890/ES12-00232.1.  & Refereed Article\\
59 & 2013 & {\bf Using atmospheric trajectories to model the isotopic composition of rainfall in central Kenya}, Soderberg, K., Good, S.P., O'Connor, M, Wang, L, Ryan, K, Caylor, K.K.. \href{https://ucsb.box.com/s/mb6z08pv5zz2vhr9kgvmoufty4vmcmgg}{[pdf]} & \emph{ Ecosphere } 4(3): 1-18. doi:10.1890/ES12-00160.1.  & Refereed Article\\
60 & 2013 & {\bf Ecosystem-scale spatial heterogeneity of stable isotopes of soil nitrogen in African savannas}, Wang, L., Okin, GS, D'Odorico, P, Caylor, K.K., Macko, S. \href{https://ucsb.box.com/s/5o5846kcmdrigqrdmwu4qxhodo3sjksi}{[pdf]} & \emph{ Landscape Ecology } 28(4): 685-698. doi:10.1007/s10980-012-9776-6.  & Refereed Article\\
61 & 2013 & {\bf The effect of warming on grassland evapotranspiration partition using laser-based isotope monitoring techniques}, Wang, L, Nui, S., Good, S.P., Soderberg, K, others, Caylor, K.K.. \href{https://ucsb.box.com/s/0jbvto99k7xct39dcnmuleikakxqs86s}{[pdf]} & \emph{ Geochemica et Cosmochimica Acta } 111: 28-38. doi:10.1016/j.gca.2012.12.047.  & Refereed Article\\
62 & 2013 & {\bf Analytical expressions of variability in ecosystem structure and function obtained from three-dimensional stochastic vegetation modelling}, Good, S.P., Rodriguez-Iturbe, I, Caylor, K.K.. \href{https://ucsb.box.com/s/abpa11ketq1heljw4jt6s1hz1y1cdvwq}{[pdf]} & \emph{ Proceedings of the Royal Society, Series A } 469(2155): 20130003. doi:10.1098/rspa.2013.0003.  & Refereed Article\\
63 & 2013 & {\bf Virtual water trade and development in Africa}, Konar, M, Caylor, K.K.. \href{https://ucsb.box.com/s/90cey1mo6xijyv8ofwgq9g18set34zmk}{[pdf]} & \emph{ Hydrology and Earth System Science } 17(10): 3969-3982. doi:10.5194/hess-17-3969-2013.  & Refereed Article\\
64 & 2013 & {\bf On The Vulnerability of Water Limited Ecosystems to Climate Change}, Manfreda, S., Caylor, K.K.. \href{https://ucsb.box.com/s/2gwcpop1y7tla777rrx5jk21wlh77520}{[pdf]} & \emph{ Water } 5(2): 819-833. doi:10.3390/w5020819.  & Refereed Article\\
65 & 2014 & {\bf Multilevel governance of irrigation systems and adaptation to climate change in Kenya }, Dell'Angelo, J, McCord, P.F., Baldwin, E., Cox, M.E., Gower, D., Caylor, K.K., Evans, T.P. & Bhaduri, A., Bogardi, J., Leentvaar, J., Marx, S. (eds.). \emph{ The Global Water System in the Anthropocene }. Springer International & Refereed Book Chapter\\
66 & 2014 & {\bf Integrating short- and long-range processes into models: The emergence of pattern}, Caylor, K.K, Okin, G.S., Turnbull, L., Wainwright, J., Wiegand, T., Franz, T.E., Parsons, A.J. & Mueller, E.N., Wainwright, J., Parsons, A.J., Turnbull, L. (eds.). \emph{ Patterns of Land Degradation in Drylands }. Springer International & Refereed Book Chapter\\
67 & 2014 & {\bf An analysis of structure: biomass structure relationships for characteristic species of the western Kalahari, Botswana}, Meyer, T, D'Odorico, P, Okin, GS, Shugart, HH, Caylor, K.K., O'Donnell FC. \href{https://ucsb.box.com/s/bsay0vhcvkmlhl04pdl7t687eflb2jlm}{[pdf]} & \emph{ African Journal of Ecology } 52(1): 20-29. doi:10.1111/aje.12086.  & Refereed Article\\
68 & 2014 & {\bf $\delta$2H Isotopic flux partitioning of evapotranspiration over a grass field following a water pulse and subsequent dry down}, Good, S.P., Soderberg, K., Guan K., King, E.G., Scanlon, TM, Caylor, K.K.. \href{https://ucsb.box.com/s/tpllvj83demjut0j70vfmrky9ag5g6yh}{[pdf]} & \emph{ Water Resources Research } 50(2): 1410-1432. doi:10.1002/2013WR014333.  & Refereed Article\\
69 & 2014 & {\bf Modelling vegetation patterns in semiarid environments}, Manfreda, S., Pizzolla, T., Caylor, K.K..  & \emph{ Procedia Environmental Sciences } 19: 168-177. doi:10.1016/j.proenv.2013.06.019.  & Refereed Article\\
70 & 2014 & {\bf Deriving vegetation phenological time and trajectory information over Africa using SEVIRI daily LAI}, Guan, K., Medvigy, D., Wood, E.F., Caylor, K.K., Li, S., Jeong, S.. \href{https://ucsb.box.com/s/djgyaaemqprp1pvy9xys5plvtubdlkwg}{[pdf]} & \emph{ IEEE Transactions on Geoscience and Remote Sensing } 52(2): 1113-1130. doi:10.1109/TGRS.2013.2247611.  & Refereed Article\\
71 & 2014 & {\bf Continental-scale impacts of intra-seasonal rainfall variability on simulated ecosystem responses in Africa}, Guan, K., Good, S.P., Caylor, K.K., Sato, Hisashui, Li, Haibin, Wood, E.F.. \href{https://ucsb.box.com/s/fhm9hn0fzw60fvm9ou7h8pduiunlf0um}{[pdf]} & \emph{ Biogeosciences } 11(23): 6939-6954. doi:10.5194/bg-11-6939-2014.  & Refereed Article\\
72 & 2014 & {\bf Changing water availability during the African maize-growing season, 1979-2010}, Estes, L, Chaney, N., Herrera-Estrada, J., Sheffield, J, Caylor, K.K., Wood, E.F.. \href{https://ucsb.box.com/s/nifv0mfgu42no30r47f9k6mqg5mm1tts}{[pdf]} & \emph{ Environmental Research Letters } 9(7): 75005. doi:10.1088/1748-9326/9/7/075005.  & Refereed Article\\
73 & 2014 & {\bf Global synthesis of vegetation control on evapotranspiration partitioning}, Wang, L., Good, S.P., Caylor, K.K., `. \href{https://ucsb.box.com/s/r5gbwjuynwn6fw8x7cd0452g4jznxfn2}{[pdf]} & \emph{ Geophysical Research Letters } 41(19): 6753-6757. doi:10.1002/2014GL061439.  & Refereed Article\\
74 & 2014 & {\bf Terrestrial hydrological controls on land surface phenology of African savannas and woodlands}, Guan, K., Wood, E.F, Medvigy, D., Wolf, A., Kimball, J., Pan, M., Caylor, K.K., Sheffield, J. \href{https://ucsb.box.com/s/ib8uckd0g1z20jt4jdtry5z2f3yarjy8}{[pdf]} & \emph{ Journal of Geophysical Research - Biogeosciences } 119(8): 1652-1669. doi:10.1002/2013JG002572.  & Refereed Article\\
75 & 2015 & {\bf Photosynthetic seasonality of global tropical forests constrained by hydroclimate}, Guan, K., Pan, M., Li, H., Wolf, A, Medvigy, D, Caylor, K.K., Sheffield, J, Wood, EF, Mahli, Y, Liang, M., others. \href{https://ucsb.box.com/s/9ycpfurog15j1632gjmn4th9uim7c4dl}{[pdf]} & \emph{ Nature Geoscience } 8(4): 284. doi:10.1038/ngeo2382.  & Refereed Article\\
76 & 2015 & {\bf Termite mounds can increase the robustness of dryland ecosystems to climatic change}, Bonachela, J.A., Pringle, RM, Shefer, E, Coverdale, TC, Guyon, JA, Caylor, K.K., Levin, SA, Tarnita, CE. \href{https://ucsb.box.com/s/v8812382lomed561t7tqpsc235lq7xpm}{[pdf]} & \emph{ Science } 347 6222): 651-655. doi:10.1126/science.1261487.  & Refereed Article\\
77 & 2015 & {\bf Carbon stable isotopes suggest that hippopotamus-vectored nutrients subsidize aquatic consumers in an East African river}, McCauley, D.J., Dawson, T, Power, ME, Finlay, JC, Ogada, M, Gower, D., Caylor, K.K.. \href{https://ucsb.box.com/s/107vvybvde5oz0nmv9vh509dmlsstaa0}{[pdf]} & \emph{ Ecosphere } 6(4): 1-11. doi:10.1890/ES14-00514.1.  & Refereed Article\\
78 & 2015 & {\bf A quantitative description of the interspecies diversity of belowground structure in savanna woody plants}, O'Donnell, F., Caylor, K.K., Bhattachan, A, Dintwe, Kebonye, D'Odorico, P, Okin, G. \href{https://ucsb.box.com/s/q8alm3n7xcpok6kfxx7tx4uq12g37972}{[pdf]} & \emph{ Ecosphere } 6(9): 1-15. doi:10.1890/ES14-00310.1.  & Refereed Article\\
79 & 2015 & {\bf Dynamic interactions of ecohydrological and biogeochemical processes in water-limited systems}, Wang, L., Manzoni, S., Ravi, S., Riveros-Iregui, D., Caylor, K.K.. \href{https://ucsb.box.com/s/41hz9m5kf175gtqdy8ac54xtl05fozl9}{[pdf]} & \emph{ Ecosphere } 6(8): 1-27. doi:10.1890/ES15-00122.1.  & Refereed Article\\
80 & 2015 & {\bf Warmer and wetter soil stimulates assimilation more than respiration in rainfed agricultural ecosystem on the China Loess Plateau: the role of partially plastic film mulching tillage}, Gong, D., Hao, W., Mei, X., Gao, X., Caylor, K.K.. \href{https://ucsb.box.com/s/bbaob5ga0fva4mmaby17wk27h12ugp3s}{[pdf]} & \emph{ PLoS One } 10(8): e0136578. doi:10.1371/journal.pone.0136578.  & Refereed Article\\
81 & 2015 & {\bf Soil organic C and total N pools in the Kalahari: potential impacts of climate change on C sequestration in savannas}, Dintwe, K., Okin, GS, D'Odorico, P, Hrast, T, Mladenov,N., Handorean, A., Bhattachan, A., Caylor, K.K.. \href{https://ucsb.box.com/s/n9o971g408g4ih9717bqd5uk42msf8k6}{[pdf]} & \emph{ Plant \& Soil } 396(1-2): 27-44. doi:10.1007/s11104-014-2292-5.  & Refereed Article\\
82 & 2016 & {\bf Global Patterns of the Contributions of Storm Frequency, Intensity, and Seasonality to Interannual Variability of Precipitation}, Good, S.P., Guan, K., Caylor, K.K.. \href{https://ucsb.box.com/s/z3yqba8scd3nc6uqgdsovlsqt0bg0a09}{[pdf]} & \emph{ Journal of Climate } 29(1): 3-15. doi:10.1175/JCLI-D-14-00653.1.  & Refereed Article\\
83 & 2016 & {\bf Improved removal of volatile organic compounds for laser-based spectroscopy of water isotopes.}, Chang, E., Wolf, A., Gerlein-Safdi, C., Caylor, K.K.. \href{https://ucsb.box.com/s/cj7itvayum95iwuvcs0a9qmauerkmlo1}{[pdf]} & \emph{ Rapid Communications in Mass Spectrometry } 30(6): 784-790. doi:doi.org/10.1002/rcm.7497.  & Refereed Article\\
84 & 2016 & {\bf Community Water Governance on Mount Kenya: An Assessment Based on Ostrom's Design Principles of Natural Resource Management}, Dell'Angelo, J, McCord, P, Gower, D., Carpenter, S., Caylor, K., Evans, T.P.. \href{https://ucsb.box.com/s/61v4ea8neqs8cwvmf7xzna1yvxk0um7j}{[pdf]} & \emph{ Mountain Research \& Development } 36(1): 102-115. doi:10.1659/MRD-JOURNAL-D-15-00040.1.  & Refereed Article\\
85 & 2016 & {\bf A platform for crowdsourcing the creation of representative, accurate landcover maps}, Estes, L, McRitchie, D., Choi, J., Debats, S., Evans, T., Guthe, W., Luo, D., Ragazzo, G., Zempleni, R., Caylor, K.K.. \href{https://ucsb.box.com/s/8nz0lvgxwpb1blrfre3brc7x7881k3hi}{[pdf]} & \emph{ Environmental Modelling \& Software } 80: 41-53. doi:10.1016/j.envsoft.2016.01.011.  & Refereed Article\\
86 & 2016 & {\bf A generalized computer vision approach to mapping crop fields in heterogeneous agricultural landscapes}, Debats, S., Luo, D., Estes, L.D., Fuchs, T., Caylor, K.K.. \href{https://ucsb.box.com/s/ss3301i5x6alzmx9xsxxyatldv3oujbr}{[pdf]} & \emph{ Remote Sensing of Environment } 179: 210-221. doi:10.1016/j.rse.2016.03.010.  & Refereed Article\\\hline\hline   &   & {\bf Since Appointment:} &    &   \\
87 & 2016 & {\bf Explaining inter-annual variability of gross primary productivity from plant phenology and physiology}, Zhou, S, Zhang, Y., Caylor, K.K., Luo, Y., Xiao, X., Ciais, P., Huang, Y., Wang, G.. \href{https://ucsb.box.com/s/dkdthi1g8ei5z7e3qeywpeptpdqhy7zf}{[pdf]} & \emph{ Agricultural \& Forest Meteorology } 226: 246-256. doi:10.1016/j.agrformet.2016.06.010.  & Refereed Article\\
88 & 2016 & {\bf Reconciling agriculture, carbon and biodiversity in a savanna transformation frontier}, Estes, L., Searchinger, T., Spiegel, M., Tian, D., Sichinga, S., Mwale, M., Kehoe, L., Kuemmerle, T., Berven, A., Chaney, N., Sheffield, J., Wood, E.F., Caylor, K.K.. \href{https://ucsb.box.com/s/59hu4x91ia3twex5r0s8ul1ave202nzk}{[pdf]} & \emph{ Philosophical Transactions of the Royal Society B - Biological Sciences } 371(1703): 20150316. doi:10.1098/rstb.2015.0316.  & Refereed Article\\
89 & 2016 & {\bf Modeling ecohydrological dynamics of smallholder strategies for food production in dryland agricultural systems}, Gower, D. B., Dell'Angelo, J., McCord, P.F., Caylor, K.K., Evans, T.P.. \href{https://ucsb.box.com/s/d5cocvrqqyl6z4by1yksxyfubg2yuyh4}{[pdf]} & \emph{ Environmental Research Letters } 11(11): 115005. doi:10.1088/1748-9326/11/11/115005.  & Refereed Article\\
90 & 2017 & {\bf An Ecohydrological Framework to Explain Shifts in Vegetation Organization Across Climatological Gradients}, Manfreda, S., Caylor, K.K., Good, S.P.. \href{https://ucsb.box.com/s/q2hupfls7zt96v7gs6e1kac7hycyfgj5}{[pdf]} & \emph{ Ecohydrology } 10(3): e1809. doi:10.1002/eco.1809 .  & Refereed Article\\
91 & 2017 & {\bf Dominant role of plant physiology in trend and variability of gross primary productivity in North America}, Zhou, S, Zhang, Y., Ciais, P, Xiao, X.M., Luo, Y.Q., Caylor, K.K., Huang, Y., Wang, G.. \href{https://ucsb.box.com/s/pc2eiwr8n6ayiqteeaz83rc14tmzyfce}{[pdf]} & \emph{ Scientific Reports } 7: 41366. doi:10.1038/srep41366.  & Refereed Article\\
92 & 2017 & {\bf Comparison of multi-level water use efficiency between plastic film partially mulched and non-mulched croplands at eastern Loess Plateau of China}, Gong, D., Mei, X., Hao, W., Caylor, K.K.. \href{https://ucsb.box.com/s/muljik4kg2ixquc1h1euhb0ennumls3p}{[pdf]} & \emph{ Agricultural Water Management } 179: 215-226. doi:10.1016/j.agwat.2016.06.006.  & Refereed Article\\
93 & 2017 & {\bf Household-level heterogeneity of water resources within common-pool resource systems}, McCord, P., Dell'Angelo, J., Gower, D., Caylor, K.K., Evans, T.. \href{https://ucsb.box.com/s/c5edgm37cq9dt58p9gz3bj6cqmyefa1z}{[pdf]} & \emph{ Ecology \& Society } 22(1). doi:10.5751/ES-09156-220148.  & Refereed Article\\
94 & 2017 & {\bf Comparison of ET partitioning and crop coefficients between partial plastic mulched and non-mulched maize fields}, Gong, D., Mei, X., Hao, W., Wang, H., Caylor, K.K.. \href{https://ucsb.box.com/s/vzrrbi417and6fo5ke33v65mgwbtpkvj}{[pdf]} & \emph{ Agricultural Water Management } 181: 23-34. doi:10.1016/j.agwat.2016.11.016.  & Refereed Article\\
95 & 2017 & {\bf Triple oxygen isotope composition of leaf waters in Mpala, central Kenya}, Li, S., Levin, N., Soderberg, K, Dennis, K.J., Caylor, K.K.. \href{https://ucsb.box.com/s/m6c6q71t2jwsbyo9q2blskcdyz29evfl}{[pdf]} & \emph{ Earth \& Planetary Science Letters } 468: 38-50. doi:10.1016/j.epsl.2017.02.015.  & Refereed Article\\
96 & 2017 & {\bf Validation of SMAP surface soil moisture products with core validation sites}, Colliander, A, Jackson, TJ, Bindish, R., others, including, Caylor, K.K.. \href{https://ucsb.box.com/s/7q3rg7qjavmnwvpi9qywmdj0dgj3ao9a}{[pdf]} & \emph{ Remote Sensing of Environment } 191: 215-231. doi:10.1016/j.rse.2017.01.021.  & Refereed Article\\
97 & 2017 & {\bf Leaf water 18O and 2H maps show directional enrichment discrepancy in Colocasia esculenta}, Gerlein-Safdi, C., Gauthier, P., Sinkler, C., Caylor, K.K.. \href{https://ucsb.box.com/s/dxtj2jm3yvcrwm5q4ne0q6ngu5z23esq}{[pdf]} & \emph{ Plant, Cell, \& Environment } 40(10): 2095-2108. doi:10.1111/pce.13002.  & Refereed Article\\
98 & 2017 & {\bf Calibration of a parsimonious distributed ecohydrological daily model in a data-scarce basin using exclusively the spatio-temporal variation of NDVI}, Ruiz-Perez, G., Kock, J., Manfreda, Salvatore, Caylor, K.K., Frances, F.. \href{https://ucsb.box.com/s/8aek3p7pfptyu9swkrj7q6s3llrxqqrh}{[pdf]} & \emph{ Hydrology and Earth System Science } 21(12): 6235-6251. doi:10.5194/hess-21-6235-2017.  & Refereed Article\\
99 & 2018 & {\bf Simulated sensitivity of African terrestrial ecosystem photosynthesis to rainfall frequency, intensity, and rainy season length}, Guan, K., Good, S.P., Caylor, K.K., Medvigy, D., Pan, Ming, Wood, E.F., Sato, H., Biasutti, M., Chen, M., Ahlstrom, A., Xiangtao, X.. \href{https://ucsb.box.com/s/3ln4mn7mtbwb6fzqi6ncxpqa5ixnniy6}{[pdf]} & \emph{ Environmental Research Letters } 13(2): 25013. doi:10.1088/1748-9326/aa9f30.  & Refereed Article\\
100 & 2018 & {\bf Measurements and Observations in the XXI century (MOXXI): innovation and multidisciplinarity to sense the hydrological cycle}, Flavia, T., Selker, J., van de Giesen, N., Abrate, T., Uijlenhoet, R., Porfiri, M., Manfreda, S., Caylor, K.K., 22 others. \href{https://ucsb.box.com/s/gm2qb4h6pypc3ik7qaqwzwn4tc3abkhx}{[pdf]} & \emph{ Hydrological Sciences Journal } 63(2): 169-196. doi:10.1080/02626667.2017.1420191.  & Refereed Article\\
101 & 2018 & {\bf A large--area, spatially continuous assessment of land cover map error and its impact on downstream analyses}, Estes, L, Chen, P., Debats, S., Evans, T., Ferreira, S., Kuemmerle, T., Ragazzo, G., Sheffield, J, Wolf, A., Wood, E.F., Caylor, K.K.. \href{https://ucsb.box.com/s/mt9dbay4vjp76mufte12dkewbbs7sctg}{[pdf]} & \emph{ Global Change Biology } 24(1): 322-337. doi:10.1111/gcb.13904.  & Refereed Article\\
102 & 2018 & {\bf The Spatial and Temporal Domains of Modern Ecology}, Estes, L, Elsen, P., Truer, T., Ahmed, L., Caylor, K.K.., Chang, J., Choi, J., Ellis, E. \href{https://ucsb.box.com/s/olvjzv8gy0hx18etd0dam75bog8yp8zp}{[pdf]} & \emph{ Nature Ecology \& Evolution } 2(5): 819. doi:10.1038/s41559-018-0524-4.  & Refereed Article\\
103 & 2018 & {\bf On the Use of Unmanned Aerial Systems for Environmental Monitoring}, Manfreda, S., McCabe, M, Miller, P., Lucas, R., Madrigal, V.P., Mallinis, G., Ben Dor, E., Helman, D., Estes, L., Ciraolo, G., 13 others including Caylor, K.. \href{https://ucsb.box.com/s/c9ee5kg0gtyqw76r897u6viu73yvxtpd}{[pdf]} & \emph{ Remote Sensing } 10(4): 641. doi:10.3390/rs10040641.  & Refereed Article\\
104 & 2018 & {\bf Dew-induced transpiration suppression impacts the water and isotope balances of Colocasialeave}, Gerlain-Safdi, C., Gauthier, P.G., Caylor, K.K.. \href{https://ucsb.box.com/s/listbal649qlgbuqa8xb4ir82pz6o3us}{[pdf]} & \emph{ Oecologia } 187(4): 1041-1051. doi:10.1007/s00442-018-4199-y.  & Refereed Article\\
105 & 2018 & {\bf Dew deposition suppresses transpiration and carbon uptake in leaves}, Gerlain-Safdi, C., Koohafkan, MC, Chung, M., Thompson, S, Rockwell, FE, Caylor, K.K.. \href{https://ucsb.box.com/s/6v2kks339czfpp06xulu1ytgjyw4oon9}{[pdf]} & \emph{ Agriculture \& Forest Meteorology } 259: 305-316. doi:10.1016/j.agrformet.2018.05.015.  & Refereed Article\\
\end{longtable}

