\documentclass[10pt]{article}
\usepackage[bottom=1in,left=1in,top=1in,right=0.75in]{geometry}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{supertabular}
\usepackage{array}
\usepackage[linkcolor=red,urlcolor=red]{hyperref}
\usepackage[official]{eurosym}

\pagestyle{fancy}
\lhead{(Page \thepage)}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}


\begin{document}

\noindent
\begin{tabularx}{\linewidth}{XX} 
BIO-BIBLIOGRAPHY & \hfill University of California, Santa Barbara \\ \\
 & \hfill June 30, 2018 \\ \\
 Kelly K. Caylor &   \\ 
 Professor II & 
 \end{tabularx}

\vspace{1cm}
% Last update filed on June 30, 2013 

This update refers to the period July 1, 2016 to June 30, 2018

\vspace{1cm}
\centering {\textbf{ \large Curriculum Vitae}}

\raggedright

\vspace{0.5cm}
\underline{Education}

University of Virginia, Ph.D., 2003

University of Virginia, B.A., 1996

\vspace{0.5cm}
\underline{Area of Specialization}

Ecohydrology, Isotope hydrology, Coupled natural-human systems, Environmental sensing.

\vspace{0.5cm}
\underline{Previous Academic or Professional Appointments}
\begin{tabular}{l p{5.5in} }
2016 - \ \ \ \ & Full Professor, Bren School of Environmental Science \& Management, UCSB \\ 
2016 - \ \ \ \ & Full Professor, Dept. of Geography, University of California, Santa Barbara \\ 
2014 - 2016 & Director, Environmental Studies Program, Princeton University \\
2013 - 2016 & Associate Professor, Dept. of Civil and Environmental Engineering, Princeton University \\
2013 - 2016 & Affiliated Faculty, Dept. of Ecology and Evolutionary Biology, Princeton University \\
2007 - 2012 \ \ \ \ & Assistant Professor, Dept. of Civil and Environmental Engineering, Princeton University \\
2007 - \ \ \ \ & Adjunct Faculty, Department of Geography, Indiana University \\ 
2005 - 2007 \ \ \ \  & Assistant Professor, Department of Geography, Indiana University \\
\end{tabular}

\vspace{0.5cm}
\underline{Professional Organizations}

American Geophysical Union, Association of American Geographers, American Association for the Advancement of Science

\vspace{0.5cm}

\textbf{PART I.  RESEARCH}

\vspace{0.2cm}
{\bf Cumulative List of Publications (or Creative Activities):}

\vspace{0.2cm}
{\setlength{\extrarowheight}{3.5pt}
\input{tex/Publications} % modified to include url to pdf instead of doi for since last review -- argh
}

\vspace{0.2cm}
{\bf Works In Press:}

\vspace{0.15cm}
{\setlength{\extrarowheight}{3.5pt}
\input{tex/InPress}
}

% \lfoot{\footnotesize *Previously listed as Work In Press; publication 43 was B-1, publication 44 was B-2.
% **Previously listed as Work Submitted. Publication 45 was C-4, publication 46 was C-1, publication 48 was C-3, and publication 50 was C-2.
 % ***Publication 51 was previously listed as Work in Progress (D-1). \\ \quad \\ Note: The doi number is an active hyperlink to the published article.}
 % \lfoot{\footnotesize Note: All doi's are active hyperlinks.}
 % 

\vspace{0.2cm}
{\bf Work Submitted:}

\vspace{0.15cm}
{\setlength{\extrarowheight}{3.5pt}
\input{tex/Submitted}
}

% \vspace{0.2cm}
% {\bf Conference Proceedings:}

% \vspace{0.15cm}
% {\setlength{\extrarowheight}{3.5pt}
% \input{Proceedings}
% }


%\clearpage
%\lfoot{}
%\vspace{0.2cm}
%{\bf Works In Progress:}
%
%\vspace{0.15cm}
%{\setlength{\extrarowheight}{3.5pt}
%\input{bib.wor}
%}
%\newpage

\vspace{1cm}
\textbf{PART II.  TEACHING (50\% Geography Dept. workload; 50\%Bren School workload. Teaching release throughout the review period.)$^1$}

\vspace{0.5cm}

\textbf{Workload Descriptions}

\begin{enumerate}
{\footnotesize

\item {\em Geography Department}: Geography department teaching workload for full-time ladder faculty is 3 Instructional Workload Courses (IWC) per year. 50\% workload is 1.5 IWC per year.

\item {\em Bren School}:  The official teaching workload in the Bren School for full-time ladder faculty members is 3.5 Instructional Workload Courses (IWC) per academic year. Full-time faculty are expected to be in residence during the academic year and teach at least two out of three quarters unless they are on sabbatical or approved leave. Each quarter on sabbatical counts as 1.17 IWC for full-time faculty. The teaching workload for faculty with partial appointments is the equivalent fraction of 3.5 and the teaching workload is negotiated with the dean.

Every full-time faculty member will advise or co-advise a Master’s Group Project (ESM 401 series) or Eco-E Project (ESM 402 series) equivalent to 1 IWC. Faculty advisors are expected to meet with master’s groups weekly during the academic year.

Course Equivalencies:
\begin{itemize}
    \item ESM 401A/ESM 402A: 4 units = 0.29 IWC 
    \item ESM 401B/ESM 402B: 4 units = 0.29 IWC
    \item ESM 401C/ESM 402C: 4 units = 0.29 IWC
    \item ESM 401D/ESM 402D: 2 units = 0.13 IWC
\end{itemize}

Every full-time faculty member will teach and/or co-teach core courses, elective courses and seminars in the MESM and PhD programs equivalent to at least (a) 2.5 IWC in addition to advising a project or (b) 3.5 IWC if not advising a project. 

Course Equivalencies:
\begin{itemize}
    \item MESM core and elective courses: 4 units = 1 IWC; 2 units = 0.5 IWC.
    \item Co-taught 4-unit MESM core course = 0.6 IWC per instructor.
    \item Co-taught 4-unit MESM elective course = 0.5 IWC per instructor.
    \item MESM lab course: 4 or 5 units = 1 IWC.
    \item Teaching an additional section (e.g., ESM 263) = 0.67 IWC.
    \item PhD core courses: ESM 510 (1 unit) = 0.25 IWC; ESM 512 (2 units) = 0.5 IWC; ESM 514 (4 units) = co-taught at 1 IWC per instructor.
    \item PhD seminar course: 2 units = 0.5 IWC; 4 units = 1 IWC.
\end{itemize}
}
\end{enumerate}

\lfoot{\footnotesize $^1$ The ERI directorship is for a 5-year term with annual reappointment.  The appointment comes with a 50\% teaching load reduction. Therefore, my four-year annual teaching load in Geography is 1-0-1-1 (an average of 0.75 IWC per year), and in Bren it is advising one group project per year, and co-teaching the MESM core course ESM 203 starting in Fall 2018 (a total of 1.6 IWC per year.}
\vspace{0.5cm}
{\bf Catalog Courses:}
\vspace{0.25cm}
\input{tex/Courses}

\vspace{0.5cm}
{\bf MESM Projects Advised}
\vspace{0.25cm}
\input{tex/MESMProjects}

\vspace{1cm}
{\bf Undergraduate Projects Directed:}
{\setlength{\extrarowheight}{3.5pt}
\tablehead{}
\begin{supertabular}{lp{11cm}cc} 
Student & Project & Chair/ & Yr Deg \\
 & & Member & Compl. \\
 \hline
%Madison Gray & History of Urban Design in Edinburgh & Chair &  2008 \\
%Eric Wilder & An assessment of environmental planning in Humboldt County, CA & Chair & 2010 \\ 
\end{supertabular}
}

\vspace{1cm}
{\bf Graduate Degree Committees, MA/MS Committees:}
\vspace{0.25cm}
\input{tex/GraduateAdvisingMS}

\vspace{0.5cm}
{\bf Graduate Degree Committees, Ph.D. Committees:}
\vspace{0.25cm}
\input{tex/GraduateAdvisingPhD}



\vspace{0.5cm}
{\bf Postdoctoral Scholars Supervised:}
\vspace{0.25cm}
\input{tex/PostdoctoralAdvising}

\lfoot{}
\vspace{0.5cm}
{\bf Other Teaching Contributions:}

None

%{\setlength{\extrarowheight}{3.5pt}
%\tablehead{}
%\begin{supertabular}{cp{16cm}} 
%- & Coordinator and instructor for the UCSB Spatial Perspectives on Curriculum Enhancement (SPACE) workshop, July 2007 \\
%- & Took the Geography 20 honors section on a field trip to UC San Diego to attend the Surfing, Arts, Sciences, and Issues Conference at Scripps Institute, February 2007 \\
%- & Mentor/advisor for Sam Boysel (San Marcos High School student) for his senior honors science project. \\
%- & Faculty undergraduate advisor, 2008-09, Geography \\
%\end{supertabular}
%}

\vspace{0.5cm}
\textbf{PART III.  PROFESSIONAL ACTIVITIES}

\vspace{0.5cm}
\textbf{Lectures Presented:}
\vspace{0.25cm}
{\setlength{\extrarowheight}{3.5pt}
\input{tex/Lectures}
}

%\newpage
\vspace{0.5cm}
\textbf{Grants and Contracts:}
\vspace{0.25cm}
{\setlength{\extrarowheight}{3.5pt}
\input{tex/Funding}
}

\vspace{0.5cm}
\textbf{Reviewing and Refereeing Activity:}
\vspace{0.2cm}
\input{tex/Reviews}

\vspace{0.25cm}
\textbf{Special Appointments:}

%\hspace{0.5cm} 2004-2008, Editorial Board, \textit{Geographical Analysis}
\hspace{0.5cm} 2016-present, Editorial Board, \textit{Environmental Research Letters, Reviews}

\vspace{0.25cm}
\textbf{Other Professional Contributions:}
\hspace{0.5cm}
\begin{tabular}{lp{2cm}p{12cm}}
% 2011-present &  Volunteer Scientist &New York City Department of Public Health.  Assisting their staff in developing methodology to improve their use of FITNESSGRAM data for monitoring, screening, and policy evaluation of childhood obesity in NYC public schools. \\
% 2015-16 & Consultant & (\$16,464) \emph{Quantile regression of longitudinal BMI growth trajectories.}, New York City Department of Health and Mental Hygiene \\
%  2015 & Participant & NSF Future Directions for Mathematics, Measurement, and Statistics Program
\end{tabular}

%\newpage

\vspace{0.5cm}
\textbf{PART IV.  SERVICE}

\vspace{0.25cm}
\textbf{University Service:}
\vspace{0.2cm}
\input{tex/UniversityService}

\vspace{0.5cm}
\textbf{Department Service:}
\vspace{0.2cm}
\input{tex/DepartmentalService}

\vspace{0.5cm}
\textbf{Public Service:}
\vspace{0.2cm}
\input{tex/ProfessionalService}



\end{document}





